Word Sense Disambiguation

### 2011-04-13 paper/methods.tex
stepwise graphs

\subsection{Identification of the best feature combinations}
We identified optimal feature combinations through backward stepwise simple linear regression
and through the creation and visual analysis of charts. The former has the
advantage of discovering relationships and testing them more quantitatively
but has the disadvantage of making assumptions about normality, linearity and equal variance.
The latter has the advantage of elucidating more complex and higher-order relationships

@@

\subsubsection{Graphical methods}

>>>>

\subsection{Identification of the best feature combinations}
We identified optimal feature combinations through backward stepwise simple linear regression
and through the creation and visual analysis of charts. The former has the
advantage of discovering relationships and testing them more quantitatively
but has the disadvantage of making assumptions about normality, linearity and equal variance.
The latter has the advantage of elucidating more complex and higher-order relationships.

@@

\subsubsection{Graphical methods}
We began by plotting the predictors that seemed most influential in the
stepwise regression.

%lassifiert, colocation, cooccurrence  
%Interpret this graph
